Improving phase-matching of FWM with temperature

### 2015-08-30 latex/article.tex
added asymmetric study

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{parcolumns}
\usepackage[left=2.cm,right=2.cm,top=2.cm,bottom=2.cm]{geometry}
\usepackage[final]{pdfpages} %serve per aggiungere altre pagine pdf al file
\usepackage{siunitx}

@@

\newpage
\section{Introduction}
\subsection{Motivation}
\subsection{Degenerate Four-Wave Mixing}
Four-Wave Mixing (FWM) is a nonlinear optical effect

\section{Linear optics}

A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\mathrm{P} = \varepsilon_0 \chi \mathrm{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.

@@

Considering an ideal dielectric waveguide (no absorption) and the total field distribution as sum of transverse electromagnetic (TEM) plane waves is possible to study the propagation of the wave along the waveguide with an electromagnetic analysis.
Furthermore it can be shown that not all field distribution are transmitted through the waveguide without energy loss.

@@

\section{Non-linear optics}
A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
$$\mathrm{P} = \varepsilon_0\chi \mathrm{E} + 2\mathrm{d}\mathrm{E}^2 + 4\chi^{(3)}\mathrm{E}^3 + \cdots$$
In everyday condition linear effects are much larger than nonlinear ones.
The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}
\subsection{Third order effect: Four-Wave Mixing}

\section{Simulating and coding ?}

>>>>

\documentclass[12pt,a4paper,twocolumn,twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{parcolumns}
\usepackage[left=2.cm,right=2.cm,top=2.cm,bottom=2.cm]{geometry}
\usepackage[final]{pdfpages} %serve per aggiungere altre pagine pdf al file
\usepackage{siunitx}

@@

\cleardoublepage 
\tableofcontents

\cleardoublepage 
\section{Introduction}
\subsection{Motivation}
\subsection{Partially degenerate Four-Wave Mixing}
Four-Wave Mixing (FWM) is a nonlinear optical effect

****
\section{Linear optics}

A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field, $\textbf{P} = \varepsilon_0 \chi \textbf{E}$, where $\varepsilon_0$ is the permittivity of free space and $\chi$ is the susceptibility of the medium.

****

@@

Considering an ideal dielectric waveguide (no absorption) and the total field distribution as sum of transverse electromagnetic (TEM) plane waves is possible to study the propagation of the wave along the waveguide with an electromagnetic analysis.
Furthermore it can be shown that not all field distribution are transmitted through the waveguide without energy loss \textbf{(?)}.

@@

\section{Non-linear optics}
A nonlinear dielectric medium is characterized by a nonlinear relation between P and E, such as
$$\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right) $$
In everyday condition linear effects are much larger than nonlinear ones.
The relation between $\mathrm{P}$ and $\mathrm{E}$ becomes nonlinear when $\mathrm{E}$ has a value comparable to interatomic electric fields, which are typically $\sim 10^5-10^8$ \si{\V\per\m}.

For an isotropic medium the second order term is zero (in the dipole approximation) and this is our scenario.
Thus the dominant nonlinearity is the third order and the material is called a Kerr medium.
\subsection{Third order effect: Four-Wave Mixing}
Many processes are result of third order nonlinearities: Third-Harmonic Generation (THG), Optical Kerr Effect, Cross-phase modulation (XPM), Self-phase modulation (SPM) and Four-Wave Mixing (FWM).

Four-Wave Mixing originates from the third order nonlinear response of a material to an electromagnetic field, precisely from the behaviour of bound electrons.
This parametric process involve nonlinear interaction among four optical waves.
\section{Simulating and coding ?}

$$\omega_1 + \omega_2 = \omega_3 + \omega_4$$
$$\omega_1 = \omega_2 = \omega_P$$
$$\omega_I = 2\omega_P - \omega_S$$
$$\Omega_S = \omega_1 + \omega_3 = \omega_4 - \omega_1$$
where we assume $\omega_3 < \omega_4$.
$$\Omega_S = |\omega_P - \omega_I| = |\omega_S - \omega_P|$$

$$\Delta k = \beta_3 + \beta_4 - \beta_1 - \beta_2$$
$$\Delta k = \beta_3 + \beta_4 - 2\beta_1$$

$$L_{coh} = \frac{2\pi}{|\Delta k|}$$
